|

### 2023-04-26 manuscript/Chapter2-appendix1.Rmd
update appendix 1

>>>>

```{r figS4, out.width = "100%", fig.cap = "**Figure S4.** Posterior median differences and 95% credible intervals in the correlations of players when they were advanced vs novice. The difference is displayed on the x axis and the parameter correlations are displayed on the y axis."}

knitr::include_graphics(
  here::here(
    "outputs", "04_outputs_figures",
    "appendix1_figureS4.png"
  )
)
